Analysis for Case 2 (habituals)

### 2018-10-08 analysis/case1-generics.Rmd
update model results and analyses

```{r generic-endorsement-priors-unbounded, eval = F}
# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time

@@

example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )
priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
  n_samples <- 10000
lg = 0
  m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 1,
                                 cores = 1,
                                 inference_opts =
                                   list(method = "MCMC",
                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))
```

@@

uncertain.threshold.model <- '
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

uncertain.threshold.model.3comp <- '
var componentParams = [
  {a: 1, b:100},
  {a: priorParams.a1, b:priorParams.b1},
  {a: priorParams.a2, b:priorParams.b2}
]
display(data.prior.mix)
display(JSON.stringify(componentParams))
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
  var component = discrete(data.prior.mix)
  // display(component)
  // display(JSON.stringify(componentParams[component]))
   var state = beta(componentParams[component])
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, verbose: T})}
'

@@

n_chains <- 2
n_samples <- 60000
burn <- n_samples / 2
lg <- 10

@@

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
}
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
#

@@

## MODEL RESULTS
load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))

@@

}
#save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')
#head(prevData)
#n_samples
```

@@

```{r}
example.generics.properties <- c("dont eat people", 
                      "carry malaria", 
                      "lay eggs", 
                      "are female",
                      "have spots")
```

@@

ggplot(gen.prev.dists, aes( x = prevalence, color = src))+
  geom_density(aes( y = ..scaled.. ))+
    #  stat_ecdf(size = 1)+
  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
   #              position = position_dodge())+
  facet_wrap(~Property + Category, nrow = 1)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

@@

```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}

# m.gen.fullmodel.prior.parameters <- m.samp %>%
#   filter(type == "prior", property %in% example.generics.properties) %>%
#   group_by(param, property, category) %>%
#   summarize(MAP = estimate_mode(val),
#             cred_upper = hdi_upper(val),
#             cred_lower = hdi_lower(val))

@@

 l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model.3comp, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model.3comp, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")

@@

m.gen.fullmodel.target.prevalence <- m.samp %>%
  filter(type == "targetPrevalence") %>%
  group_by(param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

m.gen.speakerBeliefs <- m.samp %>%
  filter(type == "targetPrevalence") %>%
  mutate(Sentence = paste(category, property)) %>%
  filter(Sentence %in% example.generics) %>%
  mutate(property = factor(property))

# m.samp.prev.params <- m.samp %>%
#     filter(type == "targetPrevalence") %>%
#     mutate(Sentence = paste(category, property)) %>%
#     filter(Sentence %in% example.generics) %>%
#     mutate(parameter = paste(param, property, category, sep = "_")) %>%
#     select(-param, -property, -category, -chain, -type) %>%
#     group_by(parameter) %>%
#     mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
#     ungroup() %>%
#     separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
#     group_by(category, property, iteration) %>%
#     spread(parameter, val) %>%
#     rowwise() %>%
#     mutate(
#       a = mean*sampleSize,
#       b = (1-mean)*sampleSize,
#       val = rbeta(n = 1, shape1 = a, shape2 = b)
#       ) %>%
#     ungroup()

gen.inset.distributions <- bind_rows(
  gen.listener.predictions %>%
    mutate(category = NA),
  m.gen.speakerBeliefs %>%
    select(property, val) %>%
    rename(value = val) %>%
    mutate(Parameter = "speakerBeliefs")
)

@@

gen.inset.distributions.refactored <- gen.inset.distributions %>%
  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior",
                                                  "speakerBeliefs"),
                            labels = c("Prevalence Prior", 
                                       "Prevalence Posterior given generalization", 
                                       "Referent Prevalence")),
         property = fct_relevel(property,
                                "have spots", "lay eggs","carry malaria", 
                                "are female", "dont eat people") )

# save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, 
#      generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
#      file = "../paper/cached_results/case1_modelPosteriors.RData")

generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
                                      aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

>>>>

```{r generic-endorsement-priors-unbounded, eval = F}
# this data set already excludes the 2nd attempt of 3 participants who completed the experiment a second time
d.gen.endorse.priors <- read.csv(paste(project.path, 
                                       "data/generics/endorsement/",
                                       "naturalGenerics-prior-trials-n57.csv", sep = ""))
gen.endorse.properties <- levels(d.gen.endorse.priors$Property)

@@

example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )

priorData <- filter(d.gen.endorse.priors, Property == "lay eggs")$prevalence
n_samples <- 10000
lg = 0
m.gen.endorse.priors.unbounded <- webppl(unboundedModel,
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 1,
                                 cores = 1,
                                 inference_opts =
                                   list(method = "MCMC",
                                        #kernel = list(HMC = list(steps = 5, stepSize = 0.001)),
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))
```

@@

uncertain.threshold.model <- '
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, burn:5000, verbose: T})}

'

uncertain.threshold.model.3comp <- '
var componentParams = [
  {a: 1, b:100},
  {a: priorParams.a1, b:priorParams.b1},
  {a: priorParams.a2, b:priorParams.b2}
]
display(data.prior.mix)
display(JSON.stringify(componentParams))
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
  var component = discrete(data.prior.mix)
  // display(component)
  // display(JSON.stringify(componentParams[component]))
   var state = beta(componentParams[component])
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, verbose: T})}
'
```

@@

n_chains <- 4
n_samples <- 100000
burn <- n_samples / 2
lg <- 20

@@

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))

}

# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
#

@@

## MODEL RESULTS
#load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))

@@

}
#save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

load("../analysis/generics-priors-posteriorPredictives.Rdata")
```

@@

```{r example generics}
example.generics.properties <- c("dont eat people", 
                      "carry malaria", 
                      "lay eggs", 
                      "are female",
                      "have spots")
```

@@

ggplot(gen.prev.dists, aes( x = prevalence, color = src))+
  geom_density(aes( y = ..scaled.. ))+
    #  stat_ecdf(size = 1)+
  #geom_histogram(aes(y=(..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
   #              position = position_dodge())+
  facet_wrap(~Property + Category, nrow = 1)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(-0.05,1.05), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(-0.01,1.01), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))

@@

```{r generic-model-insets2, fig.width = 4.75, fig.height = 1.5}
load('../analysis/generics-priors-posteriorPredictives.Rdata')
lower_bins <-seq(0, 0.975, 0.025)
upper_bins <- seq(0.025, 1, 0.025)
mid_bins <- (upper_bins - lower_bins)/2 + lower_bins

round_to_bin <- function(x){
  index <- if (x==0){ 1 } else if (x ==1){ length(mid_bins)} else{
    x <= upper_bins & x > lower_bins
  }
  #if (sum(index) > 1) { print (x) }
  return (mid_bins[index])
}

m.gen.endorse.priors.binned.i <- m.gen.endorse.priors.posteriorPredictive %>% 
  filter(src == "Data") %>%
  #group_by(property) %>%
  #sample_n(28, replace = TRUE) %>%
  #gather(category, response, -workerid, -property) %>%
  rowwise() %>%
  mutate(binned_response = round_to_bin(prevalence)) %>%
  group_by(Property, binned_response) %>%
  count() %>%
  ungroup() %>%
  spread(binned_response, n)

m.gen.endorse.priors.binned.i[is.na(m.gen.endorse.priors.binned.i)] <- 0

m.gen.endorse.priors.binned <- m.gen.endorse.priors.binned.i %>%
  gather(state, n, -Property) %>%
  group_by(Property) %>%
  mutate(prop = (n+1) / sum(n + 1),
       prop = round(prop, 5))

rsaHelpers2 <- '

var roundTo3 = function(x){
  return Math.round(x * 10000) / 10000
}

var probability = function(Dist, x) {
    return Math.exp(Dist.score(x));
}
var targetUtterance = "generic";

var bins = _.map(data.prior, "state");

var thetaBins = map2(function(b1, b2){
  return roundTo3((b2-b1)/2 + b1);
}, bins.slice(0, bins.length-1), bins.slice(1))

var priorProbs =  _.map(data.prior, "prop");

var thetaPrior = Infer({model: function(){
 return uniformDraw(thetaBins)
}});

var uncertainThresholdInterpreter = Infer({model: function(){
   var state = categorical({vs: bins, ps: priorProbs})
   factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "enumerate"})

var prior = Infer({model: function(){
   var state = categorical({vs: bins, ps: priorProbs})
    return {
      state: state, 
  }
  }, method: "enumerate"})

var returnVal = {uncertainThresholdInterpreter, prior}
returnVal
'

properties <- unique(m.gen.endorse.priors.binned$Property)
gen.listener.predictions <- data.frame()
for (p in unique(m.gen.endorse.priors.binned$Property)){

  priorProbs = m.gen.endorse.priors.binned %>% 
    filter(Property == p) %>%
    ungroup() %>%
    select(state, prop) %>%
    mutate(state = as.numeric(state))

  wp.rs <- webppl(
    program_code = rsaHelpers2, 
    data = list(prior = priorProbs, 
                utt = "generic") ,
    data_var = "data"
    )
  wp.rs.generic <- get_samples(data.frame(wp.rs$uncertainThresholdInterpreter) %>%
                                 rename(prob = probs), 10000)
  wp.rs.prior <- get_samples(data.frame(wp.rs$prior) %>%
                                 rename(prob = probs), 10000)

  gen.listener.predictions <- bind_rows(
   gen.listener.predictions, 
    wp.rs.prior  %>% mutate(property = p, Parameter = "state_Prior"),
    wp.rs.generic  %>% mutate(property = p, Parameter = "state_Posterior")
   )
}

example.generics.properties

example.generics <- c("Tigers dont eat people", 
                      "Mosquitos carry malaria", 
                      "Robins lay eggs", 
                      "Robins are female",
                      "Leopards have spots")

gen.inset.distributions <- bind_rows(
  gen.listener.predictions %>%
    mutate(category = NA),
  d.gen.endorse.priors %>% 
    mutate(Sentence = paste(Category, Property)) %>%
    filter(Sentence %in% example.generics) %>%
    select(prevalence, Property, Category) %>%
    rename(state = prevalence, property = Property, category = Category) %>%
    mutate(Parameter = "speakerBeliefs",
           state = state / 100)
)

category.text.labels <- data.frame(property = c("dont eat people", 
                      "carry malaria", "lay eggs",  "are female", "have spots"),
             category = c("Tigers", "Mosquitos", "Robins", "Robins", "Leopards"),
             x = c(0, 0.3, 0, 0, 0.3),
            y = c(3.8, 4, 4, 4, 4))

library(ggridges)
gen.inset.distributions.refactored <- gen.inset.distributions %>% filter(property %in% category.text.labels$property)

#save(gen.inset.distributions.refactored)
ggplot( gen.inset.distributions.refactored %>%
         mutate(Parameter = factor(Parameter, levels = c("state_Prior", "state_Posterior", "speakerBeliefs"),
                                   labels = c("Null interpretation\n(Prevalence prior)", "Generic interpretation\n(model)", 
                                              "Referent prevalence")),
                property = factor(property, levels = c("have spots", "lay eggs", "are female", "carry malaria", "dont eat people"))),
       aes(x = state, y = Parameter, group = Parameter ))+
  scale_y_discrete(expand = c(0.01, 0)) +   # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1), breaks = c(0, 1))  +    # for both axes to remove unneeded padding
  facet_wrap(~property, nrow = 1)+
  geom_text_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F)+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
  geom_density_ridges(scale = 1, alpha = 0.3, adjust = 1) +
  scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("")+
    theme(legend.position = "bottom", legend.title = element_blank())

```{r generic-model-insets, fig.width = 4.75, fig.height = 1.5}
# m.gen.fullmodel.prior.parameters <- m.samp %>%
#   filter(type == "prior", property %in% example.generics.properties) %>%
#   group_by(param, property, category) %>%
#   summarize(MAP = estimate_mode(val),
#             cred_upper = hdi_upper(val),
#             cred_lower = hdi_lower(val))

@@

 l0.rs.posterior <- webppl(paste(rsaHelpers, 
                                 uncertain.threshold.model.3comp, 
                                 uncertain.threshold.call, sep = '\n'), 
                           data = inputData, data_var = "data")

 l0.rs.prior <- webppl(paste(rsaHelpers, 
                             no.utterance.model.3comp, 
                             no.utterance.call, sep = '\n'), 
                       data = inputData, data_var = "data")

@@

# m.gen.fullmodel.target.prevalence <- m.samp %>%
#   filter(type == "targetPrevalence") %>%
#   group_by(param, property, category) %>%
#   summarize(MAP = estimate_mode(val),
#             cred_upper = hdi_upper(val),
#             cred_lower = hdi_lower(val))

# m.gen.speakerBeliefs <- m.samp %>%
#   filter(type == "targetPrevalence") %>%
#   mutate(Sentence = paste(category, property)) %>%
#   filter(Sentence %in% example.generics) %>%
#   mutate(property = factor(property))

m.samp.i <- m.samp %>%
    filter(type == "targetPrevalence") %>%
    mutate(Sentence = paste(category, property)) %>%
    filter(Sentence %in% example.generics) %>%
    mutate(parameter = paste(param, property, category, component, sep = "_")) %>%
    select(-param, -property, -category, -component, -chain, -type) %>%
    group_by(parameter) %>%
    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
    ungroup() %>%
    separate(parameter, into = c("parameter", "property", "category", "component"), sep= "_") %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(
      a = mean*sampleSize,
      b = (1-mean)*sampleSize,
      val = rbeta(n = 1, shape1 = a, shape2 = b)
      )

m.samp.i.mixture <- m.samp.i %>% 
    filter(component == 1) %>%
    rowwise() %>%
    mutate(c = rbinom(size = 1, n = 1, prob = mix))

m.samp.ij <- left_join(
  m.samp.i %>%
    select(Sentence, property, category, iteration, component, val) %>%
    spread(component, val),
  m.samp.i.mixture %>% select(Sentence, property, category, iteration, c)
) %>% rowwise() %>%
  mutate(prev = ifelse(c == 1, `1`, `2`))

gen.inset.distributions <- bind_rows(
  gen.listener.predictions %>%
    mutate(category = NA),
  m.samp.ij %>%
    select(property, prev) %>%
    rename(value = prev) %>%
    mutate(Parameter = "speakerBeliefs")
)

@@

gen.inset.distributions.refactored <- gen.inset.distributions %>%
  mutate(Parameter = factor(Parameter, levels = c("state_Prior",
                                                  "state_Posterior",
                                                  "speakerBeliefs"),
                            labels = c("Prevalence Prior", 
                                       "Prevalence Posterior given generalization", 
                                       "Referent Prevalence")),
         property = fct_relevel(property,
                                "have spots", "lay eggs","carry malaria", 
                                "are female", "dont eat people") )
```

```{r vizualize insets, fig.width = 8, fig.height =4}
load("../paper/cached_results/case1_modelPosteriors.RData")

# save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored,
#      generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
#      file = "../paper/cached_results/case1_modelPosteriors_moreFlexiblePrior.RData")

save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored,
     generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
     file = "../paper/cached_results/case1_modelPosteriors.RData")

#load("../paper/cached_results/case1_modelPosteriors.RData")

generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
                                      aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1.5, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    #scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

### 2018-10-08 analysis/case2-habituals.Rmd
update model results and analyses

# participant reported this in the comments section (it was recorded as a symbol)
d.hab.predictive[
  (d.hab.predictive$workerid==44 & 
     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character((response))))

@@

fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
       aes(x=logAnnualPastRate,
                              y = mean,
                              ymin = ci_lower, ymax = ci_upper,
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  guides(fill=F, shape=F)+
  scale_fill_solarized()+
  xlab("Past frequency (log scale)")+
  ylab("Predicted frequency (log scale)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

d.hab.predictive.summary
```

@@

```{r habituals-predictive-endorsement}
d.hab.predictive.endorsment <- read.csv(paste(
  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
d.hab.predictive.endorsment.catch <- read.csv(paste(
  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))

@@

d.hab.predictive.endorsment.condition.summary <- left_join(
  d.hab.predictive.endorsment, 
  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
  by = "workerid"
  ) %>% filter(pass==1) %>%
  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
  rename(item = habitual) %>%
  group_by(condition) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

@@

```{r}
save(d.hab.predictive.endorsment.summary, d.hab.predictive.summary, 
     n.subj.hab.pred.endorse, ave.seconds.hab.pred.endorse, 
     n.subj.hab.pred, ave.seconds.hab.pred, d.hab.predictive.endorsment.condition.summary, 
     lmer.rs.hab.predictive.summary,
     file = "../paper/cached_results/case2_predictive_data.RData")
```

>>>>

# participant reported this in the comments section (it was recorded as a symbol)
d.hab.predictive[
  (d.hab.predictive$workerid==44 & 
     d.hab.predictive$item=="smokes cigarettes"),"response"] <- 5
d.hab.predictive <- d.hab.predictive %>% mutate(response = as.numeric(as.character(response)))

@@

fig.hab.freq.predictive.vs.past <- ggplot(d.hab.predictive.summary,
       aes(x=logAnnualPastRate,
                              y = mean,
                              ymin = ci_lower, ymax = ci_upper,
                              fill = condition, shape=condition))+
  geom_jitter(position = position_jitter(width = .13), alpha = 0.6, size = 4)+
  scale_shape_manual(values=c(21,22,23))+
  geom_abline(intercept = 0, slope = 1, lty =3, color = 'black')+
  # #geom_errorbar(width=0.1)+
  scale_x_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-3,6),
                     breaks = c(-3, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))+  coord_fixed()+
  guides(fill=F, shape=F)+
  scale_fill_solarized()+
  xlab("Past frequency (log scale)")+
  ylab("Predicted frequency (log scale)")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

@@

```{r habituals-predictive-endorsement}
d.hab.predictive.endorsment <- read.csv(paste(
  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives.csv", sep = ""))
d.hab.predictive.endorsment.catch <- read.csv(paste(
  project.path, "data/habituals/endorsement/", "habituals-endorsement-predictives-catch_trials.csv", sep = ""))
d.hab.predictive.endorsement.filtered <- left_join(
  d.hab.predictive.endorsment, 
  d.hab.predictive.endorsment.catch %>% select(workerid, pass),
  by = "workerid"
  ) %>% filter(pass==1)  %>%
  mutate(response = ifelse(response=="agree-key", 1, 0)) %>%
  rename(item = habitual)

@@

d.hab.predictive.endorsment.condition.summary <- d.hab.predictive.endorsement.filtered %>%
  group_by(condition) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

@@

```{r}

 m.hab.predictive.endorse.summarized <- m.hab.predictive.endorse.rsa %>%
      select(-MAP, -cred_upper, -cred_lower, -src) %>% 
      unique()

d.hab.predictive.endorsement.filtered.logAnnualRates <- left_join(
  d.hab.predictive.endorsement.filtered %>% 
    select(-freqLevel, -past_logfreq, -future_logfreq),
  m.hab.predictive.endorse.summarized %>%
    select(item, condition, logAnnualPastRate, logAnnualFutureRate, future_lower, future_upper) 
)

```{r}

glm.hab.pred.endorse.pastfreq <- glm(response ~ logAnnualPastRate, 
              data = d.hab.predictive.endorsement.filtered.logAnnualRates, family = 'binomial')

glm.hab.pred.endorse.predfreq <- glm(response ~ logAnnualFutureRate, 
              data = d.hab.predictive.endorsement.filtered.logAnnualRates, family = 'binomial')

d.hab.predictive.endorsement.filtered.logAnnualRates.uniq <- unique(select(
    d.hab.predictive.endorsement.filtered.logAnnualRates, item, logAnnualPastRate, logAnnualFutureRate, future_lower, future_upper, condition
  ))

m.hab.predictive.endorse.regPastFreq <- left_join(
    m.hab.predictive.endorse.summarized,
    m.hab.predictive.endorse.summarized %>%
    mutate(
      MAP = predict(glm.hab.pred.endorse.pastfreq, ., type = "response"), 
      cred_upper = MAP,
      cred_lower = MAP,
      src = "regression_pastfreq"
      )
)

m.hab.predictive.endorse.summarized.lower <- m.hab.predictive.endorse.summarized %>%
  select(-logAnnualFutureRate) %>%
  rename(logAnnualFutureRate = future_lower)

m.hab.predictive.endorse.summarized.upper <- m.hab.predictive.endorse.summarized %>%
  select(-logAnnualFutureRate) %>%
  rename(logAnnualFutureRate = future_upper)

m.hab.predictive.endorse.regPredFreq <- left_join(
    m.hab.predictive.endorse.summarized,
    m.hab.predictive.endorse.summarized %>%
    mutate(
      MAP = predict(glm.hab.pred.endorse.predfreq, ., type = "response"), 
      cred_lower = predict(glm.hab.pred.endorse.predfreq, m.hab.predictive.endorse.summarized.lower, type = "response"),
      cred_upper = predict(glm.hab.pred.endorse.predfreq, m.hab.predictive.endorse.summarized.upper, type = "response"),
      src = "regression_futurefreq"
      )
)

m.hab.predictive.endorse.allModels <- bind_rows(
  m.hab.predictive.endorse.rsa,
  m.hab.predictive.endorse.regPredFreq,
  m.hab.predictive.endorse.regPastFreq,
  m.hab.predictive.endorse.rsa %>%
    select(-MAP, -cred_upper, -cred_lower, -src) %>%
    unique() %>%
    mutate(MAP = MAP_h, cred_lower = low,
         cred_upper = high, src = "human data")
)

```{r}
save(d.hab.predictive.endorsment.summary, d.hab.predictive.summary, 
     n.subj.hab.pred.endorse, ave.seconds.hab.pred.endorse, 
     n.subj.hab.pred, ave.seconds.hab.pred, d.hab.predictive.endorsment.condition.summary, 
     lmer.rs.hab.predictive.summary, m.hab.predictive.endorse.allModels,
     file = "../paper/cached_results/case2_predictive_data.RData")

#m.hab.predictive.endorse.allModels
```
